---
title: "Regression2"
author: "Wells"
date: "2025-12-02"
output: html_document
---


```{r}
# Set seed for reproducibility
set.seed(456)

# Create sample data for 16 students
n <- 16

# Generate number of beers (randomly assigned, typically 1-9 beers)
beers <- sample(1:9, n, replace = TRUE)

# Generate BAC values based on the regression equation with realistic noise
# BAC = -0.0127 + 0.0180 * beers + error
# We need to calibrate the error term to match the regression statistics

# Create predicted values
bac_predicted <- -0.0127 + 0.0180 * beers

# Add random error with appropriate standard deviation
# Residual standard error ≈ 0.020 (typical for this type of data)
bac <- bac_predicted + rnorm(n, mean = 0, sd =  0.0265)

# Ensure no negative BAC values
bac <- pmax(bac, 0)

# Create data frame
bac_data <- data.frame(
  student_id = 1:n,
  beers = beers,
  bac = bac
)
write_csv(bac_data, "bac_data.csv")
```


```{r}
bac_data <- read_csv("URL")

bac_data

```



```{r}
# Run the regression
model <- lm(bac ~ beers, data = bac_data)

# Display regression results
cat("\n\nRegression Results:\n")
print(summary(model))
```


```{r}

# Create scatterplot with regression line
plot(bac_data$beers, bac_data$bac,
     xlab = "Number of Beers",
     ylab = "Blood Alcohol Content (BAC)",
     main = "BAC vs Number of Beers Consumed",
     pch = 19,
     col = "darkblue")

# Add regression line
abline(model, col = "red", lwd = 2)

# Add text with regression equation
eq_text <- sprintf("BAC = %.4f + %.4f * beers", 
                   coef(model)[1], coef(model)[2])
legend("topleft", legend = eq_text, bty = "n", cex = 0.9)
```


```{r}
# ===================================================================
# EXERCISE QUESTION AND ANSWER
# ===================================================================

cat("\n\n==========================================\n")
cat("EXERCISE QUESTION:\n")
cat("==========================================\n")
cat("The correlation coefficient for number of cans of beer and BAC is 0.89.\n")
cat("Calculate R² and interpret it in context.\n\n")

# Calculate correlation coefficient from the data
r <- cor(bac_data$beers, bac_data$bac)

# Calculate R-squared
r_squared <- r^2

# Also get R-squared from the model
model_r_squared <- summary(model)$r.squared

cat("ANSWER:\n")
cat("-------\n")
cat(sprintf("Given: r = 0.89\n"))
cat(sprintf("Calculation: R² = r² = (0.89)² = %.4f\n\n", 0.89^2))

cat("From our regression model:\n")
cat(sprintf("Actual r = %.4f\n", r))
cat(sprintf("Actual R² = %.4f\n\n", model_r_squared))

cat("INTERPRETATION IN CONTEXT:\n")
cat("R² = 0.7921 means that approximately 79.2% of the variability\n")
cat("in blood alcohol content (BAC) can be explained by the number\n")
cat("of beers consumed. The remaining 20.8% of variability in BAC\n")
cat("is due to other factors not captured by this simple model,\n")
cat("such as gender, weight, drinking habits, metabolism, and\n")
cat("time since last meal.\n")
```

Questions
(a) Describe the relationship between the number of cans of beer and BAC.
(b) Do the data provide strong evidence that drinking more cans of beer is associated with an increase in blood alcohol? State the null and alternative hypotheses, report the p-value, and state your conclusion.
(c) Suppose we visit a bar, ask people how many drinks they have had, and also take their BAC. Do you think the relationship between number of drinks and BAC would be as strong as the relationship found in the Ohio State study?
